Synthesizing Symmetric Lenses

### 2018-07-08 papers/SymmetricLenses/main.tex
minor changes
edit

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \MergeLOf{\Lens_1}{\Lens_2}, \Regex}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + $\\
    &
    & $(1-\ProbabilityAlt)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2} - \Log_2(1 - \ProbabilityAlt))+$\\
    &
    & $(0, -\Log_2(\ProbabilityAlt)*\ProbabilityAlt -\Log_2(1 - \ProbabilityAlt)*(1-\ProbabilityAlt)]$\\

@@

\paragraph*{\ToStochastic} With stochastic DNF regular expressions and
\ToDNFRegex defined, it is easier to explain the function that converts regular
expressions into stochastic regular expressions, \ToStochastic. If users
specified stochastic regular expressions themselves, this step could be skipped,
though our integration into Boomerang does not permit users to provide
stochastic regular expressions. If $\Regex$ is a stochastic DNF regular
expression generated by \ToStochastic, then $\ToDNFRegexOf{\Regex} =
\DNFOf{(\Sequence_1,\frac{1}{n}) \DNFSep \ldots \DNFSep
  (\Sequence_n,\frac{1}{n})}$ for some sequences $\Sequence_1\ldots\Sequence_n$,
and every stochastic atom generated by \ToStochastic is
$\PRegexStar{\DNFRegex}{.8}$. In particular, $\ToDNFRegex$ generates regular
expressions whose DNF form gives equal probability to all sequence subcomponents
of the DNF regular expression., and gives iterations a .8 chance to continue
iterating. In our experience generating random strings from regular expressions,
these probabilities provide good distributions of strings -- stars are iterated
4 times on average, and no individual choice in a series disjunctions is chosen
disproportionately often. As we have found these distributions generate
reasonable strings, we believe they describe the shape of data well.

>>>>

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \MergeLOf{\Lens_1}{\Lens_2}, \Regex}$
    & =
    & $(0,1+\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}+\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2})$\\

@@

\paragraph*{\ToStochastic} With stochastic DNF regular expressions and
\ToDNFRegex defined, it is easier to explain the function that converts regular
expressions into stochastic regular expressions, \ToStochastic. If users
specified stochastic regular expressions themselves (perhaps inferred from
example data), this step could be skipped,
though our implementation does not (yet) permit users to provide such
stochastic regular expressions. If $\Regex$ is a stochastic DNF regular
expression generated by \ToStochastic, then $\ToDNFRegexOf{\Regex} =
\DNFOf{(\Sequence_1,\frac{1}{n}) \DNFSep \ldots \DNFSep
  (\Sequence_n,\frac{1}{n})}$ for some sequences $\Sequence_1\ldots\Sequence_n$,
and every stochastic atom generated by \ToStochastic is
$\PRegexStar{\DNFRegex}{.8}$. In particular, $\ToDNFRegex$ generates regular
expressions whose DNF form gives equal probability to all sequence subcomponents
of the DNF regular expression., and gives iterations a .8 chance to continue
iterating. In our experience generating random strings from regular expressions,
these probabilities provide good distributions of strings -- stars are iterated
4 times on average, and no individual choice in a series disjunctions is chosen
disproportionately often. As we have found these distributions generate
reasonable strings, we believe they describe the shape of data well.
